ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-26 paper/aaai/author_response.qmd

Another common concern was that *ECCCo* primiarly achieved good results for JEMs.

>>>>

Another common concern was that *ECCCo* primiarly achieved good results for JEMs. This has been addressed by introducing *ECCCo+* for situations when plausibility is crucial. We find that *ECCCo+* achieves good plausibility and faithfulness across the board. We have added convolutional neural networks to our analysis and find that *ECCCo+* achieves results for these models that are at least on par with the results for JEMs.

### 2023-09-26 paper/tables.Rmd

```{r}
for (name in unique(tab_valid$dataname)) {
  data_indicator <- gsub(" ", "-", tolower(unique(name)))
  # Choices:
  tab_full <- dcast(tab_valid[dataname==name], model + generator ~ variable)
  col_names <- c(
    "Model",
    "Generator",
    measure_names
  )
  algin_cols <- c(rep('l',3),rep('c',ncol(tab_full)-3))
  file_name <- sprintf(
    "paper/contents/table-%s-valid.tex", 
    data_indicator
  )
  cap <- sprintf(
    "All results for %s dataset: sample averages +/- one standard deviation over all valid counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (\\textit{Wachter}). \\label{tab:results-%s} \\newline",
    name,
    data_indicator
  )
  kbl(
    tab_full, caption = cap, 
    align = "c", col.names=col_names, booktabs = T, escape=F, 
    format="latex"
  ) %>%
    kable_styling(latex_options = c("scale_down")) %>%
    kable_paper(full_width = F) %>%
    collapse_rows(columns = 1:2, latex_hline = "custom", valign = "top") %>%
    save_kable(file_name)
}
```

>>>>

```{r}
for (name in unique(tab_valid$dataname)) {
  data_indicator <- gsub(" ", "-", tolower(unique(name)))
  # Choices:
  tab_full <- dcast(tab_valid[dataname==name], model + generator ~ variable)
  col_names <- c(
    "Model",
    "Generator",
    measure_names
  )
  algin_cols <- c(rep('l',3),rep('c',ncol(tab_full)-3))
  file_name <- sprintf(
    "paper/contents/table-%s-valid.tex", 
    data_indicator
  )
  cap <- sprintf(
    "All results for %s dataset: sample averages +/- one standard deviation over all valid counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (\\textit{Wachter}). \\label{tab:results-%s-valid} \\newline",
    name,
    data_indicator
  )
  kbl(
    tab_full, caption = cap, 
    align = "c", col.names=col_names, booktabs = T, escape=F, 
    format="latex"
  ) %>%
    kable_styling(latex_options = c("scale_down")) %>%
    kable_paper(full_width = F) %>%
    collapse_rows(columns = 1:2, latex_hline = "custom", valign = "top") %>%
    save_kable(file_name)
}
```
